---
title: "Machine Learning Regression Model Report - FTIR (Chicken Thigh Fillet)"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# k-Nearest Neighbours for Total Viable Counts

```{r message=FALSE, warning=FALSE}

model.knn_TVC <- readRDS("models/CTF/FTIR/model_knn_TVC.rds")
print(model.knn_TVC)
```

# Total Viable Counts distribution - k-Nearest Neighbours

```{r echo=FALSE}
test.knn<-readRDS("models/CTF/FTIR/tested_knn_TVC.rds")
RMSE.knn <- readRDS("models/CTF/FTIR/RMSE_knn_TVC.rds")
accuracy_knn_TVC <- readRDS("models/CTF/FTIR/accuracy_knn_TVC.rds")
predicted.knn <- readRDS("models/CTF/FTIR/predicted_knn_TVC.rds")

plot(predicted.knn,test.knn,xlim= c(0,9), ylim=c(0,9),xlab="Predicted bacterial counts",ylab="Actual bacterial counts",col = "blue", 
     main=paste("k-Nearest Neighbours \nRMSE:",round(RMSE.knn,digits = 2),"\nAccuracy :",round(accuracy_knn_TVC, digits = 2),"% - at ±1 LogCount"))
abline(a=0,b=1)
abline(a=-1,b=1)
abline(a=1,b=1)
```

# Linear Model for Total Viable Counts

```{r message=FALSE, warning=FALSE}
model.lm_TVC <- readRDS("models/CTF/FTIR/model_LM_TVC.rds")
print(model.lm_TVC)

```

# Total Viable Counts distribution - Linear Regression

```{r echo=FALSE}
test.lm<-readRDS("models/CTF/FTIR/tested_LM_TVC.rds")
RMSE.lm.TVC<-readRDS("models/CTF/FTIR/RMSE_LM_TVC.rds")
accuracy_lm_TVC<-readRDS("models/CTF/FTIR/accuracy_LM_TVC.rds")
predicted.lm<-readRDS("models/CTF/FTIR/predicted_LM_TVC.rds")

plot(predicted.lm, test.lm,xlim= c(0,9), ylim=c(0,9),xlab="Predicted bacterial counts",ylab="Actual bacterial counts", col="blue",
     main=paste("Linear Regression \nRMSE:",round(RMSE.lm.TVC,digits = 2),"\nAccuracy:",round(accuracy_lm_TVC, digits = 2),"% - at ±1 LogCount"))
abline(a=0,b=1)
abline(a=-1,b=1)
abline(a=1,b=1)

```

# Random Forest for Total Viable Counts

```{r message=FALSE, warning=FALSE}
model.rf_TVC <- readRDS("models/CTF/FTIR/model_RF_TVC.rds")
print(model.rf_TVC)

```

# Total Viable Counts distribution - Random Forests

```{r echo=FALSE}
test.rf<-readRDS("models/CTF/FTIR/tested_RF_TVC.rds")
RMSE.rf<-readRDS("models/CTF/FTIR/RMSE_RF_TVC.rds")
accuracy_RF_TVC<-readRDS("models/CTF/FTIR/accuracy_RF_TVC.rds")
predicted.rf<-readRDS("models/CTF/FTIR/predicted_RF_TVC.rds")

plot(predicted.rf, test.rf,xlim= c(0,9), ylim=c(0,9),xlab="Predicted bacterial counts",ylab="Actual bacterial counts", col="blue",
     main=paste("Random Forests \nRMSE:",round(RMSE.rf,digits = 2),"\nAccuracy :",round(accuracy_RF_TVC, digits = 2),"% - at ±1 LogCount"))
abline(a=0,b=1)
abline(a=-1,b=1)
abline(a=1,b=1)

```

# Support Vector Machines with Polynomial Kernel for Total Viable Counts

```{r message = FALSE, warning = FALSE}
model.svmPoly_TVC <- readRDS("models/CTF/FTIR/model_SVMP_TVC.rds")
print(model.svmPoly_TVC)

```

# Total Viable Counts distribution - Support Vector Machines with Polynomial Kernel

```{r echo=FALSE}
test.svmPoly<-readRDS("models/CTF/FTIR/tested_SVMP_TVC.rds")
RMSE.SVMP<-readRDS("models/CTF/FTIR/RMSE_SVMP_TVC.rds")
accuracy_SVMP_TVC<-readRDS("models/CTF/FTIR/accuracy_SVMP_TVC.rds")
predicted.SVMP<-readRDS("models/CTF/FTIR/predicted_SVMP_TVC.rds")

plot(predicted.SVMP,test.svmPoly,xlim= c(0,9), ylim=c(0,9),xlab="Predicted bacterial counts",ylab="Actual bacterial counts", col="blue",
     main=paste("Support Vector Machines with Polynomial Kernel \nRMSE:",round(RMSE.SVMP,digits = 2)," \nAccuracy :",round(accuracy_SVMP_TVC, digits = 2),"% - at ±1 LogCount"))
abline(a=0,b=1)
abline(a=-1,b=1)
abline(a=1,b=1)

```

# Support Vector Machines with Radial Basis Function Kernel for Total Viable Counts

```{r message = FALSE, warning = FALSE}
model.svmrad_TVC <-readRDS("models/CTF/FTIR/model_SVMR_TVC.rds")
print(model.svmrad_TVC)

```

# Total Viable Counts distribution - Support Vector Machines with Radial Basis Function Kernel

```{r echo=FALSE}
test.svmRadial<-readRDS("models/CTF/FTIR/tested_SVMR_TVC.rds")
RMSE.SVMR.TVC<-readRDS("models/CTF/FTIR/RMSE_SVMR_TVC.rds")
accuracy_SVMRAD_TVC<-readRDS("models/CTF/FTIR/accuracy_SVMR_TVC.rds")
y_pred<-readRDS("models/CTF/FTIR/predicted_SVMR_TVC.rds")

plot(y_pred,test.svmRadial,xlim= c(0,9), ylim=c(0,9),xlab="Predicted bacterial counts",ylab="Actual bacterial counts", col="blue",
     main=paste("Support Vector Machines with Radial Basis Function Kernel \nRMSE:",round(RMSE.SVMR.TVC,digits = 2)," \nAccuracy :",round(accuracy_SVMRAD_TVC, digits = 2),"% - at ±1 LogCount"))
abline(a=0,b=1)
abline(a=-1,b=1)
abline(a=1,b=1)

```

# Support Vector Machines with Linear Kernel for Total Viable Counts

```{r message = FALSE, warning = FALSE}
model.svmLM_TVC <- readRDS("models/CTF/FTIR/model_SVMLM_TVC.rds")
print(model.svmLM_TVC)

```

# Total Viable Counts distribution - Support Vector Machines with Linear Kernel

```{r echo=FALSE}
test.svmLinear<-readRDS("models/CTF/FTIR/tested_SVMLM_TVC.rds")
RMSE.SVMLM.TVC<-readRDS("models/CTF/FTIR/RMSE_SVMLM_TVC.rds")
accuracy_SVMLM_TVC<-readRDS("models/CTF/FTIR/accuracy_SVMLM_TVC.rds")
predicted.SVMLM.TVC<-readRDS("models/CTF/FTIR/predicted_SVMLM_TVC.rds")

plot(predicted.SVMLM.TVC,test.svmLinear, xlim= c(0,9), ylim=c(0,9),xlab="Predicted bacterial counts",ylab="Actual bacterial counts", col="blue",
     main=paste("Support Vector Machines with Linear Kernel \nRMSE:",round(RMSE.SVMLM.TVC,digits = 2), "\nAccuracy:",round(accuracy_SVMLM_TVC,digits = 2),"% - at ±1 LogCount"))
abline(a=0,b=1)
abline(a=-1,b=1)
abline(a=1,b=1)

```

# Linear Regression for Pseudomonas count 

```{r message = FALSE, warning = FALSE}
model.lm_Ps <- readRDS("models/CTF/FTIR/model_LM_PS.rds")
print(model.lm_Ps)

```

# Pseudomonas count distribution - Linear Regression

```{r echo=FALSE}
test.lm.ps<-readRDS("models/CTF/FTIR/tested_LM_PS.rds")
RMSE.lm.ps<-readRDS("models/CTF/FTIR/RMSE_LM_PS.rds")
accuracy_lm_PS<-readRDS("models/CTF/FTIR/accuracy_LM_PS.rds")
predicted.lm.ps<-readRDS("models/CTF/FTIR/predicted_LM_PS.rds")

plot(predicted.lm.ps, test.lm.ps,xlim= c(0,9), ylim=c(0,9),xlab="Predicted bacterial counts",ylab="Actual bacterial counts", col="blue",
     main=paste("Linear Regression \nRMSE:", round(RMSE.lm.ps,digits = 2),"\nAccuracy :",round(accuracy_lm_PS, digits = 2),"% - at ±1 LogCount"))
abline(a=0,b=1)
abline(a=-1,b=1)
abline(a=1,b=1)

```

# k-Nearest Neighbors for Pseudomonas count 

```{r message = FALSE, warning = FALSE}
model.knn_Ps <- readRDS("models/CTF/FTIR/model_knn_PS.rds")
print(model.knn_Ps)

```

# Pseudomonas count distribution - k-Nearest Neighbors

```{r echo=FALSE}
test.knn.ps<-readRDS("models/CTF/FTIR/tested_knn_PS.rds")
RMSE.knn.ps<-readRDS("models/CTF/FTIR/RMSE_knn_PS.rds")
accuracy_knn_PS<-readRDS("models/CTF/FTIR/accuracy_knn_PS.rds")
predicted.knn.ps<-readRDS("models/CTF/FTIR/predicted_knn_PS.rds")

plot(predicted.knn.ps, test.knn.ps,xlim= c(0,9), ylim=c(0,9),xlab="Predicted bacterial counts",ylab="Actual bacterial counts", col="blue",
     main=paste("k-Nearest Neighbors \nRMSE:",round(RMSE.knn.ps,digits = 2),"\nAccuracy :",round(accuracy_knn_PS, digits = 2),"% - at ±1 LogCount"))
abline(a=0,b=1)
abline(a=-1,b=1)
abline(a=1,b=1)

```

# Random Forests for Pseudomonas count  

```{r message = FALSE, warning = FALSE}
model.rf_Ps <- readRDS("models/CTF/FTIR/model_RF_PS.rds")
print(model.rf_Ps)

```

# Pseudomonas count distribution - Random Forests

```{r echo=FALSE}
test.rf.ps<-readRDS("models/CTF/FTIR/tested_RF_PS.rds")
RMSE.rf.ps<-readRDS("models/CTF/FTIR/RMSE_RF_PS.rds")
accuracy_RF_PS<-readRDS("models/CTF/FTIR/accuracy_RF_PS.rds")
predicted.rf.ps<-readRDS("models/CTF/FTIR/predicted_RF_PS.rds")

plot(predicted.rf.ps,test.rf.ps,xlim= c(0,9), ylim=c(0,9),xlab="Predicted bacterial counts",ylab="Actual bacterial counts", col="blue",
     main=paste("Random Forests \nRMSE:",round(RMSE.rf.ps,digits = 2),"\nAccuracy :",round(accuracy_RF_PS, digits = 2),"% - at ±1 LogCount"))
abline(a=0,b=1)
abline(a=-1,b=1)
abline(a=1,b=1)

```

# Support Vector Machines with Polynomial Kernel for Pseudomonas count 

```{r message = FALSE, warning = FALSE}
model.svmPoly_Ps <- readRDS("models/CTF/FTIR/model_SVMP_PS.rds")
print(model.svmPoly_Ps)

```

# Pseudomonas count distribution - Support Vector Machines with Polynomial Kernel

```{r echo=FALSE}
test.svmPoly.ps<-readRDS("models/CTF/FTIR/tested_SVMP_PS.rds")
RMSE.SVMP.ps<-readRDS("models/CTF/FTIR/RMSE_SVMP_PS.rds")
accuracy_SVMP_PS<-readRDS("models/CTF/FTIR/accuracy_SVMP_PS.rds")
predicted.SVMP.PS<-readRDS("models/CTF/FTIR/predicted_SVMP_PS.rds")

plot(predicted.SVMP.PS,test.svmPoly.ps,xlim= c(0,9), ylim=c(0,9),xlab="Predicted bacterial counts",ylab="Actual bacterial counts", col="blue",
     main=paste("Support Vector Machines with Polynomial Kernel \nRMSE:",round(RMSE.SVMP.ps,digits = 2),"\nAccuracy :",round(accuracy_SVMP_PS, digits = 2),"% - at ±1 LogCount"))
abline(a=0,b=1)
abline(a=-1,b=1)
abline(a=1,b=1)

```

# Support Vector Machines with Linear Kernel for Pseudomonas count 

```{r message = FALSE, warning = FALSE}
model.svmLM_Ps <- readRDS("models/CTF/FTIR/model_SVMLM_PS.rds")
print(model.svmLM_Ps)

```

# Pseudomonas count distribution - Support Vector Machines with Linear Kernel

```{r echo=FALSE}
test.svmLinear.ps<-readRDS("models/CTF/FTIR/tested_SVMLM_PS.rds")
RMSE.SVMLM.ps<-readRDS("models/CTF/FTIR/RMSE_SVMLM_PS.rds")
accuracy_SVMLM_PS<-readRDS("models/CTF/FTIR/accuracy_SVMLM_PS.rds")
predicted.SVMLM.PS<-readRDS("models/CTF/FTIR/predicted_SVMLM_PS.rds")

plot(predicted.SVMLM.PS,test.svmLinear.ps,xlim= c(0,9), ylim=c(0,9),xlab="Predicted bacterial counts",ylab="Actual bacterial counts", col="blue",
     main=paste("Support Vector Machines with Linear Kernel \nRMSE:",round(RMSE.SVMLM.ps,digits = 2),"\nAccuracy :",round(accuracy_SVMLM_PS, digits = 2),"% - at ±1 LogCount"))
abline(a=0,b=1)
abline(a=-1,b=1)
abline(a=1,b=1)

```


# Support Vector Machines with Radial Basis Function Kernel for Pseudomonas count

```{r message = FALSE, warning = FALSE}

model.svmrad_Ps <-readRDS("models/CTF/FTIR/model_SVMR_PS.rds")
print(model.svmrad_Ps)

```

# Pseudomonas count distribution - Support Vector Machines with Radial Basis Function Kernel

```{r echo=FALSE}
test.svmRadial.ps<-readRDS("models/CTF/FTIR/tested_SVMR_PS.rds")
RMSE.SVMR.ps<-readRDS("models/CTF/FTIR/RMSE_SVMR_PS.rds")
accuracy_SVMRAD_PS<-readRDS("models/CTF/FTIR/accuracy_SVMR_PS.rds")
y_pred.ps<-readRDS("models/CTF/FTIR/predicted_SVMR_PS.rds")

plot(y_pred.ps, test.svmRadial.ps,xlim= c(0,9), ylim=c(0,9),xlab="Predicted bacterial counts",ylab="Actual bacterial counts", col="blue",
     main=paste("Support Vector Machines with Radial Basis Function Kernel \nRMSE:",round(RMSE.SVMR.ps,digits = 2),"\nAccuracy :",round(accuracy_SVMRAD_PS, digits = 2),"% - at ±1 LogCount"))
abline(a=0,b=1)
abline(a=-1,b=1)
abline(a=1,b=1)

```
